Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/inverted_u.tex
edits

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}
\section{Competition vs Better Algorithms}\label{section:5}
\swedit{how about just name the section ``inverted U''?}  \swedit{Now
  we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. \gaedit{We break indifference between exploration algorithms and non-exploration algorithms towards non-exploration algorithms.} First, the story for permanent monopoly is relatively straightforward.}

>>>>

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}
\section{Competition vs Better Algorithms}\label{section:5}
\swcomment{how about just name the section ``inverted U''?}  \swedit{Now
  we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. \gaedit{We break indifference between exploration algorithms and non-exploration algorithms towards non-exploration algorithms.} First, the story for permanent monopoly is relatively straightforward.}
